Expanding the Power of Lens Synthesis With Annotations

### 2019-02-07 papers/BXProposal/main.tex
add main

>>>>

While we have shown how these annotations can work for quotient lenses, we could
even imagine getting them to work for symmetric lenses. If we viewed symmetric
lenses as also having a bijective core (with projections on both sides instead
of just one), providing \lstinline{skip} annotations on the right could even
make synthesizing symmetric lenses easier. Of course, this would require
symmetric lenses in Boomerang for the generated lenses to be well-typed.
